Non-kissing complexes and tau-tilting for gentle algebras

### 2018-09-07 firstPaper/firstPaperLong/nonKissingComplex.tex
minor modif Proposition 3.68

Conversely, for a non-self-kissing walk~$\omega \in \NKWalks^\pm(\bar Q)$ not in the peak facet, the inclusion minimal string in the set~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$ is denoted by~$\sigma_\bottom(\omega)$.
\end{definition}

\begin{proposition}
\label{prop:bijectionDistinguishableStringsWalks}
The maps~$\omega_\bottom$ and~$\sigma_\bottom$ are inverse bijections between the distinguishable strings of~$\bar Q$ and the bending walks of~$\walks^\pm(\bar Q)$ not in the peak facet~$F_\peak$.
\end{proposition}

>>>>

Conversely, for a bending non-self-kissing walk~$\omega \in \NKWalks^\pm(\bar Q)$ not in the peak facet, the inclusion minimal string in the set~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$ is denoted by~$\sigma_\bottom(\omega)$.
\end{definition}

\begin{proposition}
\label{prop:bijectionDistinguishableStringsWalks}
The maps~$\omega_\bottom$ and~$\sigma_\bottom$ are inverse bijections between the distinguishable strings of~$\bar Q$ and the bending non-self-kissing walks of~$\NKWalks^\pm(\bar Q)$ not in the peak facet~$F_\peak$.
\end{proposition}

### 2018-09-07 firstPaper/firstPaperShort/nonKissingComplex.tex
minor modif Proposition 3.68

Conversely, for a non-self-kissing walk~$\omega \in \NKWalks^\pm(\bar Q)$ not in the peak facet, we denote by~$\sigma_\bottom(\omega)$ the inclusion minimal string in~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$.
\end{definition}

\begin{proposition}
\label{prop:bijectionDistinguishableStringsWalks}
The maps~$\omega_\bottom$ and~$\sigma_\bottom$ are inverse bijections between the distinguishable strings of~$\bar Q$ and the bending walks of~$\walks^\pm(\bar Q)$ not in the peak facet~$F_\peak$.
\end{proposition}

>>>>

Conversely, for a bending non-self-kissing walk~$\omega \in \NKWalks^\pm(\bar Q)$ not in the peak facet, we denote by~$\sigma_\bottom(\omega)$ the inclusion minimal string in~$\set{\sigma \in \Sigma_\bottom(\omega)}{\closure{\Sigma_\bottom(\omega)} = \closure{\Sigma_\bottom(\sigma)}}$.
\end{definition}

\begin{proposition}
\label{prop:bijectionDistinguishableStringsWalks}
The maps~$\omega_\bottom$ and~$\sigma_\bottom$ are inverse bijections between the distinguishable strings of~$\bar Q$ and the bending non-self-kissing walks of~$\NKWalks^\pm(\bar Q)$ not in the peak facet~$F_\peak$.
\end{proposition}
